On Secure Delegation of SampBQP with a Classical Client

### 2019-12-23 hamiltonian.tex
Make editorial change

\begin{definition}
	Call $C$ an $HT$-circuit if it consists of only Hadamard and Toffoli gates.
\end{definition}

\begin{theorem}
	Given a circuit $C$ and classical input $x$, a $\BPP$ machine can reduce it to an $HT$-circuit $C'$ and classical input $x'$.
\end{theorem}

@@

$L$ can be thought of as how ``local" the Hamiltonian is. Taking $L=5$ would easily suffice for this paper.

\begin{definition}
	Let $C(x)$ be an $HT$-circuit. Then let $H_{C(x)}$ be with the following properties:
	\begin{itemize}
		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$ with at most $O(T)$ terms
		\item Has an eigenvector $\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t\ldots U_1\ket{x}\otimes\ket{\hat{t}}$ with eigenvalue $0$.
		\item Let $\ket\phi$ be such that $\braket{\phi|\psi_{C(x)}}=0$, then $\braket{\phi|H_{C(x)}|\phi}>\frac{3}{4}$.
	\end{itemize}
\end{definition}

@@

\begin{theorem}
	Given $HT$-circuit $C$ and classical $x$, a $\BPP$ machine can construct a description of $H_{C(x)}$ in polynomial time.
\end{theorem}

\begin{theorem}
	Given $HT$-circuit $C$ and $x$, there exists an quantum algorithm that accepts $\ket{\psi_{C(x)}}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}$. Furthermore, this algorithm doesn't apply any quantum gates, and uses only $X$ and $Z$ measurements.
\end{theorem}

@@

\begin{observation}
	\label{idpadding}
	Given $HT$-circuit $C$ and $x$, one can first pad $C$ with identity matrices at the end, doubling its number of gates and obtain $C'$. One can then measure the last register of $\psi_{C'(x)}$ and obtain with probabiliy $\frac{1}{2}$ the state $C(x)$.
\end{observation}

\subsection{$HT$-circuits}

Here we prove that $HT$-circuits are universal. After this subsection, we'll be able to assume without loss of generality that all quantum circuits are $HT$-circuits.

We pick our universal gate set to be Hadamard gate and controlled phase gate following \cite{quant-ph/0301040}:
$$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
	$$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$
		Which is proven to be universal in \cite{kitaev_1997}.

@@

\begin{proof}

	Consider the transform on quantum states
	$$\mathcal{F}(\ket{\phi})=(\Re\ket{\phi})\otimes\ket{0}+(\Im\ket{\phi})\otimes\ket{1}$$
	where $\Re$ and $\Im$ denote real and imaginary parts respectively.

@@

Here we reduce a circuit into a local Hamiltonian instance with a few additional properties.

\begin{theorem}
	Let $C=U_T\ldots U_1$ be a $HT$-circuit, and let $x\in\set{0, 1}^*$. Then a classical machine can construct in polynomial time descriptions of some $H_{C(x)}\in\spn\mathcal{G}_{XZ}$ such that:
	\begin{itemize}
		\item its ground state is $$\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
		\item $\braket{\psi_{C(x)}|H_{C(x)}|\psi_{C(x)}}=0$
		\item $\forall\ket\phi,\braket{\phi|\psi_{C(x)}}=0\Rightarrow\braket{\phi|H_{C(x)}|\phi}\geq\frac{3}{4}$
		\item Has $O(T)$ nonzero components whose coefficients are each at most $O(T^3)$.
	\end{itemize}
\end{theorem}

@@

\subsection{Measuring ground state}

>>>>

\begin{theorem}
	Given a circuit $C$ and classical input $x$, a $\BPP$ machine can reduce it to another circuit $C'$ and classical input $x'$, where $C'$ contains only Hadamard and Toffoli gates.
\end{theorem}

@@

$L$ can be thought of as how ``local" a Hamiltonian is. Taking $L=5$ would easily suffice for this paper.

\begin{definition}
	Let $C(x)$ be a circuit consisting of Hadamard and Toffoli gates. Then let $H_{C(x)}$ be with the following properties:
	\begin{itemize}
		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$ with at most $O(T)$ terms
		\item Has an eigenvector $\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t\ldots U_1\ket{x}\otimes\ket{\hat{t}}$ with eigenvalue $0$.
		\item Let $\ket\phi$ be such that $\braket{\phi|\psi_{C(x)}}=0$, then $\braket{\phi|H_{C(x)}|\phi}>\frac{3}{4}$.
	\end{itemize}
\end{definition}

@@

\begin{theorem}
	Given circuit $C$ consisting of Hadamard and Toffoli gates, and $x\in\set{0,1}^*$, a $\BPP$ machine can construct a description of $H_{C(x)}$ in polynomial time.
\end{theorem}

\begin{theorem}
	Given circuit $C$ consisting of Hadamard and Toffoli gates, and $x\in\set{0,1}^*$, there exists an quantum algorithm that accepts $\ket{\psi_{C(x)}}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}$. Furthermore, this algorithm doesn't apply any quantum gates, and uses only $X$ and $Z$ measurements.
\end{theorem}

@@

\begin{observation}
	\label{idpadding}
	Given circuit $C$ and $x$, one can first pad $C$ with identity matrices at the end, doubling its number of gates and obtain $C'$. One can then measure the time register of $\ket{\psi_{C'(x)}}$ and obtain with probability $\frac{1}{2}$ the state $C(x)$.
\end{observation}

\subsection{Circuits of Toffoli and Hadamard gates}

Here we first prove that $\set{H, T}$ is a universal gate set. After this subsection, we'll be able to assume without loss of generality that all quantum circuits consists of only Toffoli and Hadamard gates. After doing that, we make a further observation that we'll use later.

We know that Hadamard gate and controlled phase gate is universal following \cite{quant-ph/0301040}:
$$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
	$$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$
		Which is proven to be universal in \cite{kitaev_1997}.

@@

\begin{proof}
	Consider the transform on quantum states
	$$\mathcal{F}(\ket{\phi})=(\Re\ket{\phi})\otimes\ket{0}+(\Im\ket{\phi})\otimes\ket{1}$$
	where $\Re$ and $\Im$ denote real and imaginary parts respectively.

@@

Here we reduce a circuit into a history XZ local Hamiltonian instance.

\begin{theorem}
	Let $C=U_T\ldots U_1$ be a circuit consisting of Hadamard and Toffoli gates, and let $x\in\set{0, 1}^*$. Then a classical machine can construct in polynomial time descriptions of some $H_{C(x)}\in\spn\mathcal{G}_{XZ}$ such that:
	\begin{itemize}
		\item its ground state is $$\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
		\item $\braket{\psi_{C(x)}|H_{C(x)}|\psi_{C(x)}}=0$
		\item $\forall\ket\phi,\braket{\phi|\psi_{C(x)}}=0\Rightarrow\braket{\phi|H_{C(x)}|\phi}\geq\frac{3}{4}$
		\item Has $O(T)$ nonzero components whose coefficients are each at most $O(T^3)$.
	\end{itemize}
\end{theorem}

@@

\subsection{Checking for ground state}

### 2019-12-23 qpip.tex
Add introductory details for qpip
Add TODO for QPIP reference

Here we create a QPIP scheme for...  In the case for decision problems, it would be a simple Chernoff bound as in \cite{kitaev2002classical}. A prover, honest or not, couldn't do better than sending $n$ identical copies of some state. The same reasoning does not generalize to our case, so instead we give the following construction.

We first give an alternative characterization of $\QPIP_0$.

\begin{definition}
	A sampling problem $S=(D_x)$ is said to be in $\QPIP_{XZ}$, or has a $\QPIP_{XZ}$ protocol,  with completeness $c$ and soundness $(\delta, s)$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
	\begin{itemize}
		\item $\bbP$ is a $\BQP$ machine.
		\item $\bbV$ is a hybrid quantum-classical machine. Its classical part is a $\BPP$ machine. Its quantum part is a single-qubit register, on which the verifier can apply only $X$ or $Z$ measurements.
		\item There is a quantum channel between $\bbP$ and $\bbV$ that can transmit one qubit at a time.
		\item There is a classical communication channel between $\bbP$ and $\bbV$.
		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
		\item (Soundness) Given $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$'s outputs has distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
	\end{itemize}
\end{definition}

\begin{theorem}
	$\QPIP_{XZ}=\QPIP_0$
\end{theorem}
\begin{proof}
	See \cite{mahadev_delegation}.
\end{proof}

\begin{theorem}
	There is a $\QPIP_{XZ}$ protocol for \autoref{AlgGroundStateCheck}
\end{theorem}
\begin{proof}
	The prover simply sends the input qubit-by-qubit for the verifier to measure. It is obvious that any attacks on this scheme trivially maps onto an attack on the original scheme.
\end{proof}

\begin{theorem}
	$\SampBQP$ is in $\QPIP_{XZ}$ with completeness negligible to perfect and soundness $(O(T^{-c}), 1-O(T^{-c}))$ for any constant $c$.
\end{theorem}
\begin{proof}
	Set the following variables
	\begin{itemize}
		\item $\varepsilon=T^{-c}$
		\item $m$ large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
		\item $n$ large enough so by Chernoff bound:
			\begin{itemize}
				\item[$\circ$] $q'=P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$ is negligible in $\varepsilon$
				\item[$\circ$] $P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$ is negligible in $\varepsilon$
			\end{itemize}
		\item $N$ large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
	\end{itemize}

	We claim that the following protocol does what is required:
	\floatname{algorithm}{Protocol}
	\begin{algorithm}
		\caption{Our $\QPIP_{XZ}$ protocol}
		\label{AlgAmp1}
		\begin{algorithmic}[1]
			\State The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
			\State The verifier randomly picks $n+m$ copies in sequence and without replacement
			\State The verifier runs \autoref{AlgGroundStateCheck} on $n$ of the copies
			\If{over $(\frac{1}{2}-\varepsilon)n$ copies accept}
			\For{$i\gets 1, m$}
				\State Measure the time register of a fresh copy from the prover
				\If{Measured $t\geq T$}
					\State Measure and output its data register
				\EndIf
			\EndFor
			\State Reject
			\Else
			\State Reject
			\EndIf
		\end{algorithmic}
	\end{algorithm}

@@

	All errors up to this point is $O(\varepsilon)$.

\end{proof}

>>>>

Here we create a $\QPIP_1$ scheme for $\SampBQP$ by constructing a history XZ local Hamiltonian instance, and ask the prover to provide the ground state. In the case for decision problems, it would be a simple Chernoff bound as in \cite{kitaev2002classical}. A prover, honest or not, couldn't do better than sending $n$ identical copies of some state. The same reasoning does not generalize to our case, so instead we give the following construction.

We then extend our scheme for $\QPIP_0$, by using results from \cite{mahadev_delegation}.

\subsection{TODO 1 qubit}

\Ethan{Fix title}

First, we make an observation.

\begin{observation}
	There is a $\QPIP_1$ protocol for \autoref{AlgGroundStateCheck}. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
\end{observation}
\begin{proof}
	The prover simply sends the input qubit-by-qubit for the verifier to measure. It is clear that any attacks on this scheme trivially maps onto an attack on the original scheme.
\end{proof}

\begin{theorem}
	Let $L\in\SampBQP$. Then there exists some $\QPIP_1$ protocol for $L$ with completeness negligible to perfect and soundness $(O(T^{-c}), 1-O(T^{-c}))$ for any constant $c$. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
\end{theorem}
\begin{proof}
	Set the following variables
	\begin{itemize}
		\item $\varepsilon=T^{-c}$
		\item $m$ large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
		\item $n$ large enough so by Chernoff bound:
			\begin{itemize}
				\item[$\circ$] $q'=P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$ is negligible in $\varepsilon$
				\item[$\circ$] $P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$ is negligible in $\varepsilon$
			\end{itemize}
		\item $N$ large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
	\end{itemize}

	We claim that the following protocol does what is required:
	\floatname{algorithm}{Protocol}
	\begin{algorithm}
		\caption{Our $\QPIP_{XZ}$ protocol}
		\label{AlgAmp1}
		\begin{algorithmic}[1]
			\State The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
			\State The verifier randomly picks $n+m$ copies; $m$ for output and $n$ for checking
			\State $c\gets0$
			\For{$i\gets1, N$}
			    \If{Register is for checking}
			    \State The verifier runs \autoref{AlgGroundStateCheck} on the register
			    \If{Test passes}
			        $c\gets c+1$
			    \EndIf
			    \ElsIf{Register is for outputting}
			    \State The verifier measures the clock register
			    \If{measurement result $\geq\frac{T}{2}$}
			        \If{$y$ isn't set}
			            $y\gets$ Measure the data register
                    \EndIf
			    \EndIf
			    \Else
			    \State Measure the entire register in standard basis
			    \EndIf
			\EndFor
			\If{$\frac{c}{n}\geq\frac{1}{2}-\varepsilon$}
			\If{$y$ is set}
			\State output $y$
			\Else
			\State Reject
			\EndIf
			\Else
			\State Reject
			\EndIf
		\end{algorithmic}
	\end{algorithm}

@@

	All errors up to this point is $O(\varepsilon)$.
\end{proof}

\subsection{TODO 0 qubits}

\Ethan{Fix title}
